NoTitle

### 2017-06-12 Aplas17/sections/Formalization.tex
Revising overview.
add tex for proof and move proofs to Appendix

>>>>

\subsection{Properties}
Previously the definitions of our model are given, now we should proceed to prove the type soundness of 
the model, which relates typing to computation. We want to prove such a property: if an expression is 
well-typed, then after many reduction steps it must reduces to a value of a subtype of the original type
of the expression. Following the FeatherweightJava paper~\cite{Igarashi01FJ}, the type-soundness theorem 
(Theorem~\ref{theorem_soundness}) is proved by using the standard technique of subject reduction (Theorem~\ref{theorem_subject})
and progress (Theorem~\ref{theorem_progress})~\cite{Wright1994}.

\begin{theorem}[Subject Reduction]~\label{theorem_subject}
$\textit{If } \ \judgeewf \Gamma {e : I} \; \textit{ and } \ e \rightarrow e',\ 
\textit{then } \judgeewf \Gamma {e' : I'} \ \textit{ for some } \ I' <: I.$
\end{theorem}
\begin{proof}
See Appendix~\ref{appendix_proof}.
\end{proof}

\begin{theorem}[Progress]~\label{theorem_progress}
$\textit{Suppose } e \textit{ is a well-typed expression } $ \\
\begin{enumerate}
\item If $e$ includes $\left(<J>\new{I}\right).m(\overline{<I_E>} \; \overline{e})$ as a subexpression,
    then $ \mbody(m, I, J) = (\overline{I_X} \; \overline{x}, I'_E \; e_0) $ and
         $\num{\overline{x}} = \num{\overline{e}}$ for some $\overline{I_X}, \overline{x}, I_E'$ and $e_0$
\item If $e$ includes $\left(<J>\new{I}\right).K::m(\overline{<I_E> e})$ as a subexpression,
    then $ \mbody(m, I, K) = (\overline{I_X} \; \overline{x}, I'_E \; e_0) $ and 
         $\num{\overline{x}} = \num{\overline{e}}$ for some $\overline{I_X}, \overline{x}, I_E'$ and $e_0$
\item If $e$ includes $\kwsuper.K::m(\overline{<I_E> e})$ as a subexpression,
    then $ \mbody(m, K, K) = (\overline{I_X} \; \overline{x}, I'_E \; e_0) $ and 
         $\num{\overline{x}} = \num{\overline{e}}$ for some $\overline{I_X}, \overline{x}, I_E'$ and $e_0$
\end{enumerate}
\end{theorem}
\begin{proof}
See Appendix~\ref{appendix_proof}.
\end{proof}

\begin{theorem}[Type Soundness]~\label{theorem_soundness}
If $\judgeewf \o {e : I}$ and $e \to^* e'$ with $e'$ a normal form, then $e'$ is 
a value $v$ with $\judgeewf \o {v:J}$ and $J \subtype I$.
\end{theorem}
\begin{proof}
Immediate from Theorem~\ref{theorem_subject} and Theroem~\ref{theorem_progress}.
\end{proof}

### 2017-06-12 Aplas17/sections/RelatedWork.tex
add tex for proof and move proofs to Appendix

\noindent {\bf Self.} In the prototype-based language \self~\cite{Chambers1991}, inheritance is a basic feature.
It does not include classes but instead allow individual objects to inherit from (or delegate to) other objects. 
Although it is different than class-based languages, the multiple inheritance model is somehow similar. The \self 
language support multiple (object) inheritance in a clever way. Not only the new inheritance
relation \emph{prioritized parents} is developed, but also the method lookup rule called 
\emph{sender path tiebreaker rule}, which is similar with our approach, using hirarchical 
information in method resolution, but in a prototype-based language setting.

\subsection{Static+Dynamic Type Method Lookup}

>>>>

\subsection{Hirarchical Dispatch}
As we have discussed before, the mix of static and dynamic dispatch is needed by the literature 
pay little attention to this. In the prototype-based language \self~\cite{Chambers1991}, inheritance is a basic feature.
It does not include classes but instead allow individual objects to inherit from (or delegate to) other objects. 
Although it is different than class-based languages, the multiple inheritance model is somehow similar. The \self 
language support multiple (object) inheritance in a clever way. Not only the new inheritance
relation \emph{prioritized parents} is developed, but also the method lookup rule called 
\emph{sender path tiebreaker rule}, which is similar with our approach, using hirarchical 
information in method resolution, but in a prototype-based language setting.
